Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-08-01 apj.tex
forging onward

Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
heavily extinguished by host-galaxy dust.
Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
   \label{perobject:fig}}
\end{figure}

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
\color{purple}
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
0.00^{+0.06}_{-0.06} & 1 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
-0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.06^{+0.08}_{-0.08} \\
-0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1 \\
\end{array}
\end{pmatrix}.
\end{multline}
\color{black}

We find weak correlations between our color-excess parameters and the input features; 
\color{purple}
only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
\color{black}
Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
and \citet{leget:thesis}.

@@

The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
the former.

@@

\color{purple}
Our linear model would be satisfied by any two independent vectors  that span
the plane defined by the $\pmb{\gamma}$ vectors.  We begin discussion on the specific choice of $\pmb{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model. 
While
Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\mathbf{a}$ and $\mathbf{b}$ and
their corresponding parameters 
$A_V$ and 
$E(B-V)$, the linear dust model could be written in terms of any two other basis vectors  $\mathbf{a}+\kappa_1 \mathbf{b}$
and $\kappa_2 \mathbf{a} + \mathbf{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
In this basis, the model is then
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.

Our posterior
includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction. This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.   We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
the effective total-to-selective extinction of our sample.
\color{purple}
The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\pmb{\gamma}^0$ and  $\mathbf{a}+\mathbf{b}/2.44$.
From the Monte Carlo chains, we find a 68\% credible interval for  $R^F_{eff}$ of 2.26--2.63.

Different supernovae are expected to encounter dust with different $R^F$.
Let us introduce a new per-supernova vector $\delta R$ such that $R^F = R^F_{eff}(1+  \delta R)$.
Variations in the value of $R^F$ (and hence $\delta R$) lead 
the prior to  determine $\kappa_2$ as 
\begin{equation}
\kappa_2 = R^F_{eff} \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
\end{equation}
From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R\, E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))$.  This result indicates that there is a small but significant covariance between  extinction contributions due to
fractional deviations from an effective $R^F$ and
the color-excess parameter $E^F(B-V)$.

@@

\color{black}
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
%   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
%   \caption{
%   Two perspectives of $UVI$- spaces
%of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
%   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
%   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
%   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
%   lines, the former is 
%   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
%   \label{plane_sim:fig}}
%\end{figure}
%

Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values of $\gamma^0_V k_0$ 
\color{purple}
relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
\color{black}
The distribution is non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.  This distribution is given by the data, in that it is independent of any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

Figure~\ref{k0_med:fig} also shows the distribution of $\gamma^1_V k_1$
relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$, which can be attributed to 
extinction corrections due to deviations away from the canonical $R^F_{eff}$ value.   The distribution has a long
negative tail and is peaked at its positive edge. Recall that our model constraints force 
the distribution of $\gamma^1_V k_1$ has a mean of zero.
The implication is that while the bulk of supernovae have positive values associated with $R>1/\kappa_1$, there is a tail
of negative values associated with $R<1/\kappa_1$.  The plot of   $\gamma^0_V k_0$ versus $\gamma^1_V k_1$  shown in Figure~\ref{kk:fig} shows that
the positive edge in $\gamma^1_V k_1$ persists over the full range of  $\gamma^0_V k_0$
%\color{purple}
%While at low  $\gamma^0_V k_0$
%\color{black}
%On the other hand, lower values of $\gamma^1_V k_1$
%occur at larger values of  $\gamma^0_V k_0$.
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
%\citet{2011ApJ...729...55F} and the above authors
%find that supernovae with large extinction 
%preferentially exhibit low $R^F$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
      \caption{
      \color{purple} Normalized ideogram and histogram 
      of
median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
which  is associated with extinction corrections due to deviations away from the canonical $\kappa_1$ value (right).
      \color{black}
   \label{k0_med:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/deltakk.pdf}
      \caption{
      \color{purple}
      $\gamma^1_V k_1-\gamma^0_V k_0|_0$ versus $\gamma^0_V k_0-\gamma^1_V k_1|_0$.
      \color{black}
   \label{kk:fig}}
\end{figure}
%
%The model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%are projected onto the  \citetalias{1999PASP..111...63F} values of $E^F(B-V)$ and $A^F$, up to an additive constant:  these are shown in Figure~\ref{avebv:fig}.
%The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.24 \pm 0.16$.  
%The linear fit also produces the zeropoint, allowing us to determine individual $R^F_V$ for all supernovae,
%which are shown in Figure~\ref{avebv_synth:fig}.   The relative values of the projected parameters are similar to
%the native $R_V$, $A_V$, and $E(B-V)$  shown in Figure~\ref{avebv:fig}.
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.8in]{output11/avebv_synth.pdf}
%   \includegraphics[width=2.8in]{output11/avrv_synth.pdf}
%    \caption{Left: Projections of our model parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)$ for the supernovae in our sample
%onto the  \citetalias{1999PASP..111...63F} dust-model plane.  Note that the error bars do not capture the strong
%covariance between the parameters. Right: $R^F_V$ for each supernova.
%   \label{avebv_synth:fig}}
%\end{figure}
%

%
%Another comparison between our model predictions with those of dust is presented in
%Figure~\ref{avebv:fig}, which shows the expectations for measured $A(V)$, $E(B-V)$ for $R^F=1.1, 1.9, 2.5, 3.1$.
%Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
%non-linear.
%Qualitatively, the $R^F \sim 2.4$  most closely matches our linear model fit.

The near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that our  supernova
parameters translate to  \citetalias{1999PASP..111...63F} parameters with consistent distributions, lead us to conclude that 
$\{k_0, k_1\}$, describe for the most part the $\{ E(B-V), R\}$ parameters used
in standard models of Milky Way dust.  Yet there do remain some small inconsistencies between our numbers and expectations from dust models.

@@

Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E(U_o-V_o) =   2.23 \pm   0.03$,
$E(B_o-V_o) =   1.28 \pm   0.04$,
$E(R_o-V)_o =  -0.47 \pm   0.03$,
$E(i_o-V_o) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ emphasizes that this is an observed color excess.
The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
wavelengths 
3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
and those used for the observations,
these data are fit to our model
\begin{equation}
E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
\end{equation}
where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and the fit
parameters $e_i $.

@@

In the fit to our model, the observed color excess is attributed to 
%----
$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
%---
$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$ 
%---
(see Figure~\ref{ebv:fig}).
The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span of supernovae used to train the coefficients of the model, which is not unexpected if
attributable to dust.

\color{purple}
The model parameters can be transformed into  the 
\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
of our model are  shown in Figure~\ref{sn2014j:fig}. 
Our model predictions provide a significantly better match to the data
despite the only approximate correspondence of the synthetic SNfactory and \citet{2014ApJ...788L..21A} observer passbands.
Differences in the color predictions between our model and the pure dust model are
apparent,
particularly in the $B-V$ and  $R-V$ colors.  Our model has shallower decline in color excess with increasing wavelength.
(Refer to  Eqn.~\ref{res_I:eqn} to see the deviation in magnitude of our model away from the dust model.)
The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
Notwithstanding their bias respect to the data, we present the transformed dust parameters
$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.430 & -0.004 \\
-0.004 & 0.007
\end{array}
\end{pmatrix},
\end{equation}
which imply $R^F= 0.59^{+ 0.53}_{-0.48}$.

>>>>

%Each supernova is described by its parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)=(\gamma^0_B-\gamma^0_V)k_0$, and
%$E_{\gamma^1}(B-V)=(\gamma^1_B-\gamma^1_V)k_1$, as well as its grey offset
%$\Delta$: their distributions for all Monte Carlo links for all supernovae are shown in Figure~\ref{perobject:fig}.
%There is a core concentration in the  parameter-space, with around ten objects that occupy its outskirts.
%Many outliers appear in the red tail of $E_{\gamma^0}(B-V)$, as would be expected for the (infrequent) selection of supernovae
%heavily extinguished by host-galaxy dust.
%Outliers  are also clearly distinguishable in  $EW_{Ca}$--$\lambda_{Si}$ space.   
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output11/perobject_corner.pdf} 
%   \caption{Distributions for the supernova parameters $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$, as well as the grey offset
%$\Delta$.  All Monte Carlo links are plotted, so that each supernova contributes a cloud of points.
%   \label{perobject:fig}}
%\end{figure}

Each supernova is described by its parameters $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^1}(B-V)$.
Their Pearson correlation coefficients  are given in the matrix
\color{purple}
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1 & 0.00^{+0.06}_{-0.06} & -0.07^{+0.07}_{-0.06} & -0.04^{+0.06}_{-0.06} & 0.10^{+0.07}_{-0.07} & -0.00^{+0.08}_{-0.07} \\
0.00^{+0.06}_{-0.06} & 1 & 0.10^{+0.03}_{-0.03} & -0.26^{+0.03}_{-0.03} & -0.07^{+0.06}_{-0.06} & -0.01^{+0.08}_{-0.08} \\
-0.07^{+0.07}_{-0.06} & 0.10^{+0.03}_{-0.03} & 1 & -0.14^{+0.04}_{-0.03} & -0.17^{+0.05}_{-0.05} & -0.04^{+0.08}_{-0.07} \\
-0.04^{+0.06}_{-0.06} & -0.26^{+0.03}_{-0.03} & -0.14^{+0.04}_{-0.03} & 1 & 0.03^{+0.05}_{-0.06} & 0.03^{+0.08}_{-0.08} \\
0.10^{+0.07}_{-0.07} & -0.07^{+0.06}_{-0.06} & -0.17^{+0.05}_{-0.05} & 0.03^{+0.05}_{-0.06} & 1 & 0.06^{+0.08}_{-0.08} \\
-0.00^{+0.08}_{-0.07} & -0.01^{+0.08}_{-0.08} & -0.04^{+0.08}_{-0.07} & 0.03^{+0.08}_{-0.08} & 0.06^{+0.08}_{-0.08} & 1 \\
\end{array}
\end{pmatrix}.
\end{multline}
\color{black}

We find weak correlations between our color-excess parameters and the input features; 
\color{purple}
only the $ -0.17 \pm 0.05$ between $E_{\gamma^0}(B-V)$ and $EW_{Si}$ has significance much larger than $1 \sigma$.
\color{black}
The feature $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
and \citet{leget:thesis}.

@@

\color{purple}
The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All  vectors are set to intersect the origin.
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
vectors span near-parallel planes in the 5-dimensional color space, and hence the latter can be almost entirely expressed in terms of
the former.

@@

Our linear model would be satisfied by any two independent vectors  that span
the plane defined by the $\pmb{\gamma}$ vectors.  We begin discussion on the specific choice of $\pmb{\gamma}$  returned by the fit within the context of the \citetalias{1999PASP..111...63F}  dust model. 
While
Eqn.~\ref{f99:eqn} expresses that model using basis vectors $\mathbf{a}$ and $\mathbf{b}$ and
their corresponding parameters 
$A_V$ and 
$E(B-V)$, the linear dust model could be written in terms of any two other basis vectors  $\mathbf{a}+\kappa_1 \mathbf{b}$
and $\kappa_2 \mathbf{a} + \mathbf{b}$ as parameterized by $\kappa_1$ and $\kappa_2$.
In this basis, the model is then
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\label{newdust:eqn}
\end{equation}
with the new parameters $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$  equal to  linear combinations of the original parameters.

Our posterior
includes a prior in which the per-supernova parameters $k_0$ and  $k_1$ associated with $\gamma$ are uncorrelated.
The parameters $\kappa_1$ and $\kappa_2$ are set by this prior.
If the external parameters of our model were indeed described by the \citetalias{1999PASP..111...63F}  dust model, then the prior corresponds
to    $A^F_V - \kappa_2 E^F(B-V)$ and $-\kappa_1 A^F_V + E^F(B-V)$ being uncorrelated in the supernova sample.
A trivial scenario that produces non-correlation is one in which all supernovae have the same parameter value for $-\kappa_1 A^F_V + E^F(B-V)$.
All color changes would then be confined to the $a(X)+\kappa_1 b(X)$ direction. This scenario corresponds to the \citetalias{1999PASP..111...63F}  dust model restricted to a constant $R^F=\kappa_1^{-1}$.   We use this interpretation to assign  $R^F_{eff} = \kappa_1^{-1}$ as
the effective total-to-selective extinction of our sample.
The preferred values for $\kappa$ can be determined from the matrix elements of Eqn.~\ref{trans_I:eqn}: $\kappa^{-1}_1=2.82/1.15 =2.44$.
Figure~\ref{plane:fig} visualizes the near-perfect alignment of $\pmb{\gamma}^0$ and  $\mathbf{a}+\mathbf{b}/2.44$.
From the Monte Carlo chains, we find a 68\% credible interval for  $R^F_{eff}$ of 2.26--2.63.

Given the association of  our parameter $\gamma^0_V k_0$ with changes in $A^F_V$ of an $R^F =\kappa^{-1}_1$ dust model up to an additive offset,
the former's distribution can be compared to the expectation for the latter.
Figure~\ref{k0_med:fig} shows the histogram of
median values and the ideogram of $\gamma^0_V k_0$ 
relative to that of an arbitrary supernova  $\gamma^0_V k_0|_0$.
(Subtracting the value of the one supernova suppresses correlated errors in $k_0$ common to all supernovae.)
The distributions are non-Gaussian, having a sharp rise in the blue and an extended tail in the red.  This is consistent
with the expectation of dust based on the spatial distribution of supernovae within galaxies and the distribution of galaxy orientations with respect to the observer \citep{1998ApJ...502..177H}.  This distribution is given by the data, and so is not dependent of any knowledge or prior
for the distribution of dust extinction the SN population is expected to suffer.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/deltagamma0_med.pdf}
   \includegraphics[width=2.8in]{output11/deltagamma1_med.pdf}
      \caption{
      \color{purple} Normalized ideogram and histogram 
      of
median values of $\gamma^0_V k_0-\gamma^0_V k_0|_0$, which are associated with the $A^F_V$ of an $R^F \sim 1/\kappa_1$ dust model
(left) : $\gamma^1_V k_1-\gamma^1_V k_1|_0$,
which  is associated with extinction corrections due to deviations away from the canonical $R^F_{eff}$ value (right).
      \color{black}
   \label{k0_med:fig}}
\end{figure}

We now consider the direction of $\pmb{\gamma}^1$. 
Different supernovae are expected to encounter dust with different $R^F$;
having  associated $\pmb{\gamma}^0$ with an $R^F_{eff}$, $\pmb{\gamma}^1$ is associated with perturbations
away that effective value.
Let us introduce a new parameter for each supernova $\delta R$ such that its $R^F = R^F_{eff}(1+  \delta R)$.
Variations in the value of $R^F$ (and hence $\delta R$) with the prior of the non-correlation between $k_0$ and $k_1$ lead 
to 
\begin{equation}
\kappa_2 = R^F_{eff} \left(1- \frac{\mbox{Var}(\delta R\, E^F(B-V))}{\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))}\right).
\end{equation}
From the matrix elements of Eqn.~\ref{trans_I:eqn},  $\kappa_2=-5.27/0.72=-7.31$, so that $\mbox{Var}(\delta R\, E^F(B-V)) = 4.00\times\mbox{Cov}(\delta R\, E^F(B-V), E^F(B-V))$.  This result indicates that there is a small but significant covariance between  extinction contributions due to
fractional deviations from an effective $R^F$ and
the color-excess parameter $E^F(B-V)$.
Figure~\ref{k0_med:fig} shows the histogram of median values and ideogram of $\gamma^1_V k_1$
relative to that of an arbitrary supernova  $\gamma^1_V k_1|_0$.

Perhaps a more instructive way to consider $k_1$ is to not view it in isolation, but rather as part of a $\{k_0,k_1\}$ pair.
A matrix such as the one in  Eqn.~\ref{trans_I:eqn} is used to transform this pair into an $\{A_V^F, E^F(B-V)\}$ pair
(modulo additive constants)  for each link in the Monte Carlo chains. A plot showing the expected values and 68\% credible intervals of these parameters
for our supernova
sample is shown in Figure~\ref{kk:fig}. 
For reference, a line that represents $R^V_{eff}=2.44$ is overplotted.  The majority of supernovae lie within a narrow range above the line
meaning they have $R^F > R^V_{eff}$,
while the remaining fraction fall in a broader range below the line for an $R^F < R^V_{eff}$.  
These findings are consistent with previous results:
\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F<3$ encountered by the SN~Ia population.
A per supernova determination $R^F$ requires the specification of the magnitude and colors of supernovae that experience
no dust, which is unspecified in our model.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/avebv_synth.pdf}
      \caption{
      \color{purple}
      Expected values and 68\% credible intervals of effective $E^F(B-V)$ and $A_V^F$ after transformation from our model $k_0$ and $k_1$ parameters, for the supernova in our sample.
      Overplotted is a line with the slope expected for $R^F=2.44$.
      \color{black}
   \label{kk:fig}}
\end{figure}

@@

To summarize, in this subsection
we conclude that the combination of
$\{k_0, k_1\}$ describe for the most part the combination of the $\{A^F_V, E^F(B-V)\}$ parameters used
in standard models of Milky Way dust.  
This conclusion is based on the
near coplanarity of the plane defined by our parameters and the plane of  \citetalias{1999PASP..111...63F}, together with the fact that 
the distribution of $k_0$ is consistent with the expected distribution of $A^F_V$.
Nevertheless, there do remain some small inconsistencies between our numbers and expectations from dust models.
\color{black}

@@

Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E(U_o-V_o) =   2.23 \pm   0.03$,
$E(B_o-V_o) =   1.28 \pm   0.04$,
$E(R_o-V)_o =  -0.47 \pm   0.03$,
$E(i_o-V_o) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}, where the subscript $o$ denotes that this is an observed color excess.
The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
wavelengths 
3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
and those used for the observations,
these data are fit to our model
\begin{equation}
E(X_o-V_o) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)e_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)e_1,
\end{equation}
where we use the median values of the $\pmb{\gamma}$- and $\pmb{\delta}$-terms from Table~\ref{global:tab} and $e_i $ are the fit
parameters.

@@

In the fit to our model, the observed color excess is attributed to 
%----
$E_{\gamma^0}(B-V)=  0.90 \pm   0.08$ and  $E_{\gamma^1}(B-V)=  0.34 \pm   0.10$
%-----
contributions.
Among the supernovae in the SNfactory  set used to determine $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$, the
objects with extreme median MCMC-sample values in $E_{\gamma^0}(B-V)$ have 
%---
$-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$, and in $E_{\gamma^1}(B-V)$  have $-0.01 \pm 0.01$  and
$  0.06 \pm 0.03$. 
%---
The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span of supernovae used to train the coefficients of the model, which is not unexpected if
attributable to dust.

\color{purple}
The  parameters $E_{\gamma^0}(B-V)$ and  $E_{\gamma^1}(B-V)=  0.34$ can be transformed into  the 
\citetalias{1999PASP..111...63F} parameters using the transpose of the matrix in Eqn.~\ref{trans_I:eqn},
assuming that  SN~2011fe has zero extinction.  The colors predicted by this \citetalias{1999PASP..111...63F}--component
of our model are  shown in Figure~\ref{sn2014j:fig}. 
Significant differences between the projection and the data is apparent
in the $B-V$ and  $R-V$ colors.
The data and the full model both have shallower decline in color excess with increasing wavelength.
The difficulty that  the  \citetalias{1999PASP..111...63F} model has in accounting for SN~2014J colors within the optical range is also evident
in Figure 3 of  \citet{2014ApJ...788L..21A}, who fit
UV through NIR data to obtain $R_V^F=1.4$ and $E^F(B-V)=1.37$.
Notwithstanding their bias respect to the data, we present the transformed dust parameters
$A^F_V=0.77$ and $E^F(B-V)=1.28$ and covariance
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.430 & -0.004 \\
-0.004 & 0.007
\end{array}
\end{pmatrix},
\end{equation}
which together give $R^F= 0.59^{+ 0.53}_{-0.48}$.
\color{black}
